The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-16 document/ms.tex
some words about the box model

\newcommand{\modelname}[1]{{\textsf{#1}}}

@@

>>>>

\newcommand{\modelname}[1]{{\textsf{#1}}}
\newcommand{\datareleaseurl}{url to be added at submission}

@@

Since the search procedure described here was tuned to discover transit
signals, we do not consider the distribution or potential astrophysical nature
of any models besides the \modelname{transit} model.
In the future, it would be interesting to relax this goal and investigate the
other model classes because, for example, the \modelname{box} model is
probably sensitive to other astrophysical phenomena like secondary eclipses.
In a cursory investigation it is clear that the majority of signals labeled
\modelname{box} in our analysis are noise but a subset are likely to be
astrophysical in nature.
